---
title: "Retrieving NYT"
author: "Jihyeon bae"
date: "2023-02-02"
output: html_document
---

#For future reference, if any of the below code does not work, it is because of the NYT's very narrow call limit. Try slicing time windows (perhaps fetching article for a month) and then add pieces together. Can reach out to the NYT API team directly for better call limit. Otherwise, default will be 200 pages. 

```{r setup, include=FALSE}
#install.packages("devtools")
#devtools::install_github("mkearney/nytimes")


library(plm)
library("pacman")
p_load(plyr, dplyr, ggplot2, MASS, tidyverse, magrittr, RColorBrewer, readxl,
  readr, rtweet, lubridate, scales, leaflet, academictwitteR, ggmap, quanteda,
  ggmap, jtools, jsonlite, haven, lmerTest, sjPlot, sjmisc, modelsummary, stargazer, tmap, terra, rgdal, httr, yaml, nytimes, plm)


```

#Setting up API
```{r}
Sys.setenv(NYTIMES_KEY="PUT YOUR API KEY HERE")
NYTIMES_KEY="PUT YOUR API KEY HERE"

```



```{r}

term <- "trump" # Need to use + to string together separate words
begin_date <- "20161108"
end_date <- "20210108"

baseurl <- paste0("http://api.nytimes.com/svc/search/v2/articlesearch.json?q=",
                  "&begin_date=",20161108,
                  "&end_date=",20161108,
                  "&facet_filter=true&api-key=",NYTIMES_KEY, sep="")

initialQuery <- fromJSON(baseurl)

maxPages <- round((initialQuery$response$meta$hits[1] / 10)-1) 

pages <- list()
for(i in 0:maxPages){
  nytSearch <- fromJSON(paste0(baseurl, "&page=", i), flatten = TRUE) %>% data.frame() 
  message("Retrieving page ", i)
  pages[[i+1]] <- nytSearch 
  Sys.sleep(10) 
}

sample <- rbind_pages(pages)


```

# This creates a separate data frame that gives the count of articles published per day. I used for loop to fetch the total number of pages gathered for each day. 

```{r}
daily_nyt<-data.frame(matrix(ncol=2))
colnames(daily_nyt) <-c("date", "count")

start <-format(as.Date("2016-01-08"), "%Y%m%d")
end <- format(as.Date("2021-01-08"), "%Y%m%d")

dates <-seq(from=start, to=end, by=1)


for (d in dates){
  baseurl <- paste0("http://api.nytimes.com/svc/search/v2/articlesearch.json?q=",
                  "&begin_date=",d,
                  "&end_date=",d,
                  "&facet_filter=true&api-key=",NYTIMES_KEY, sep="")
  initialQuery <- fromJSON(baseurl)
  output = c(d, round((initialQuery$response$meta$hits[1] / 10)-1))
  daily_nyt<-rbind(daily_nyt, output)
    d <-d + 1
  Sys.sleep(6) 
}


```



